---
title: "Pasta: Noodlyfied Pasting of Strings"
author: "Christoph Schürz, Daniel Klotz"
date: "`r Sys.Date()`"
output:
  knitr:::html_vignette:
    number_sections: yes
vignette: >
  %\VignetteIndexEntry{Pasta: Noodlyfied Pasting of Strings}
  %\VignetteEngine{knitr::rmarkdown_notangle}
  %\VignetteEncoding{UTF-8}
---

# Introduction 
Base R provides a functionality to concatenate strings through the `paste` 
functions. Using paste is nice and dandy, but the code can get quite difficult
to read. Especially if two paste functions need to be nested.

**Pasta** provides a set of infix functions to make concatenation noodlier. 
This can make the code more in intuitive and readable. Here are
some tasty examples of the provided functionality:
```{r}
  require(pasta, quietly = TRUE)
  #
  examples <- c(
  'macaroni' %_% 'sauce',
  'ravioli' %-% 'recipe',
  'spaghetti' %.% 'code',
  'fussili' %//% 'farfalle',
  'pasta' %&% 'sciutta',
  'noodle' %&&% 'soup',
  'carbonara' %|% 'ragù',
  'spaghetti' %&&% 'al' %-% 'dente'
  )
  print(examples)
```


# Dishes
Some less-naive exmaples: 

Assume you have a folder with screen-captures of the last spaghetti western you 
watched and u want to make an animation out of some carefully chosen pictures. 

```{r, eval = FALSE}
  setwd("your wd")
  cap_url <- "http://www.caps.media/195/9-rio-bravo/full/rio-bravo-movie-screencaps.com"
  jpg_urls <- c(cap_url %-% c(4,5,264:268) %.% "jpg")
  for (i in 1:length(jpg_urls)) {
      download.file(jpg_urls[i], c("test" %_% i %.% "jpg"), mode = "wb")
    
  }



```

